\bf Comparing the Power of Plot Designs to Reveal Correlation

### 2016-01-11 paper/paper.Rnw
Updates

\begin{table}[htp]
\caption{Weighted Mixed Effects Logit Model for the predicted power of plot design. Sample size for scatter plot evaluations: 900, overlaid lines: 949, total: 1849. Default plot design is overlaid lines. The model is fitted using the GLIMMIX procedure in SAS.}
\label{tab1}
\centering
<<powerfit, dependson='setup', results='asis', echo=FALSE, message=FALSE, error=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
sasdata <- select(full.sub, rabs, n, alpha, rsgn, smoothed, design, subj_id, weights, correct, log_time)
sasdata$rabs <- as.numeric(sasdata$rabs)
sasdata$subj_id <- as.numeric(sasdata$subj_id)
sasadata <- mutate(sasdata, design = ifelse(design=="Scatterplot", 1, 0))
#write.csv(subsetted, "sas/choices.csv", row.names = FALSE)
powercoef <- powercoef[,-1]
rownames(powercoef) <- c("Intercept", "abs(r)", "sign(r)", "abs(r)*sign(r)", "smoothed", "t", "plot", "plot*abs(r)", "plot*sign(r)", "plot*abs(r)*sign(r)", "plot*smoothed", "plot*t")
colnames(powercoef) <- c("Estimate", "standard error", "df", "t-value", "p-value")
kable(powercoef, format="latex", digits=2)
@
\end{table}

@@

\begin{table}[htp]
\caption{Linear mixed model fit for time taken to make a selection, default plot style is overlaid lines. Fitted with the MIXED procedure in SAS.}
\label{tab2}
\centering
<<timefit, dependson='setup', results='asis', echo=FALSE, message=FALSE, error=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
time.fit <- time.fit[c(1, 5, 6, 2, 3, 4, 7, 8, 12, 13, 9, 10, 11, 14),] #separate into main effects then interaction effects in same order
rownames(time.fit) <- c("Intercept", "Smoothed", "t", "abs(r)", "sign(r)", "abs(r)*sign(r)", "detected", "design", "design*Smoothed", "design*t", "design*abs(r)", "design*sign(r)", "design*abs(r)*sign(r)", "design*detected")
time.fit$Effect <- NULL
colnames(time.fit) <- c("Estimate", "standard error", "df", "t-value", "p-value")
kable(time.fit[1:14,], format="latex", digits=2)
@
\end{table}

@@

\begin{figure}[htbp]
\centering
<<map, dependson='setup', echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
location <- read.csv("location.csv")
map.dat <- map_data("world")
ggplot() + geom_polygon(aes(long,lat, group=group), fill="grey65", data=map.dat) + theme_bw() +
  geom_point(data=location, aes(x=lon, y=lat, colour= "blue")) +scale_colour_manual(values=c("#FF5500", "#00FFFF")) + theme(axis.text=element_blank(), axis.title=element_blank(), legend.position="none")
@
\label{map}
\end{figure}

>>>>

\begin{table}[htp]
\caption{Weighted Mixed Effects Logit Model for the predicted power of plot design. Sample size for scatter plot evaluations: 900, overlaid lines: 949, total: 1849. Default plot design is overlaid lines. The model is fitted using the GLIMMIX procedure in SAS.}
\label{tab1}
\centering
<<powerfit, dependson='setup', results='asis', echo=FALSE, message=FALSE, error=FALSE, warning=FALSE>>=
sasdata <- select(full.sub, rabs, n, alpha, rsgn, smoothed, design, subj_id, weights, correct, log_time)
sasdata$rabs <- as.numeric(sasdata$rabs)
sasdata$subj_id <- as.numeric(sasdata$subj_id)
sasadata <- mutate(sasdata, design = ifelse(design=="Scatterplot", 1, 0))
#write.csv(subsetted, "sas/choices.csv", row.names = FALSE)
powercoef <- powercoef[,-1]
rownames(powercoef) <- c("Intercept", "abs(r)", "sign(r)", "abs(r)*sign(r)", "smoothed", "t", "plot", "plot*abs(r)", "plot*sign(r)", "plot*abs(r)*sign(r)", "plot*smoothed", "plot*t")
colnames(powercoef) <- c("Estimate", "standard error", "df", "t-value", "p-value")
kable(powercoef, format="latex", digits=2)
@
\end{table}

@@

\begin{table}[htp]
\caption{Linear mixed model fit for time taken to make a selection, default plot style is overlaid lines. Fitted with the MIXED procedure in SAS.}
\label{tab2}
\centering
<<timefit, dependson='setup', results='asis', echo=FALSE, message=FALSE, error=FALSE, warning=FALSE>>=
<<answertables, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
time.fit <- time.fit[c(1, 5, 6, 2, 3, 4, 7, 8, 12, 13, 9, 10, 11, 14),] #separate into main effects then interaction effects in same order
rownames(time.fit) <- c("Intercept", "Smoothed", "t", "abs(r)", "sign(r)", "abs(r)*sign(r)", "detected", "design", "design*Smoothed", "design*t", "design*abs(r)", "design*sign(r)", "design*abs(r)*sign(r)", "design*detected")
time.fit$Effect <- NULL
colnames(time.fit) <- c("Estimate", "standard error", "df", "t-value", "p-value")
kable(time.fit[1:14,], format="latex", digits=2)
@
\end{table}

@@

\begin{figure}[htbp]
\centering
<<answertables, dependson='setup', echo=FALSE, results='asis', message=FALSE, error=FALSE, warning=FALSE>>=
location <- read.csv("location.csv")
map.dat <- map_data("world")
ggplot() + geom_polygon(aes(long,lat, group=group), fill="grey65", data=map.dat) + theme_bw() +
  geom_point(data=location, aes(x=lon, y=lat, colour= "blue")) +scale_colour_manual(values=c("#FF5500", "#00FFFF")) + theme(axis.text=element_blank(), axis.title=element_blank(), legend.position="none")
@
\label{map}
\end{figure}
